---
title: "R Notebook"
output:
  html_document:
    df_print: paged
---
Iris - Neural Network Demo
Vitor, Milton
December 13, 2017
published in: https://rpubs.com/vitorhs/iris

Loading Package and treating the data

```{r}
data(iris)
iris$setosa <- iris$Species=="setosa"
iris$virginica <- iris$Species == "virginica"
iris$versicolor <- iris$Species == "versicolor"
iris.train.idx <- sample(x = nrow(iris), size = nrow(iris)*0.5)
iris.train <- iris[iris.train.idx,]
iris.valid <- iris[-iris.train.idx,]
```

Network Aplication

```{r}
library(neuralnet)
iris.net <- neuralnet(setosa+versicolor+virginica ~ 
                      Sepal.Length + Sepal.Width + Petal.Length + Petal.Width, 
                      data=iris.train, hidden=c(10,10), rep = 5, err.fct = "ce", 
                      linear.output = F, lifesign = "minimal", stepmax = 1000000,
                      threshold = 0.001)
```


```{r}
plot(iris.net, rep="best")

```

Predicting Result

```{r}
iris.prediction <- compute(iris.net, iris.valid[-5:-8])
idx <- apply(iris.prediction$net.result, 1, which.max)
predicted <- c('setosa', 'versicolor', 'virginica')[idx]
table(predicted, iris.valid$Species)
```

When you save the notebook, an HTML file containing the code and output will be saved alongside it (click the *Preview* button or press *Ctrl+Shift+K* to preview the HTML file).

The preview shows you a rendered HTML copy of the contents of the editor. Consequently, unlike *Knit*, *Preview* does not run any R code chunks. Instead, the output of the chunk when it was last run in the editor is displayed.
